\tool: Revisiting BadUSB with Type-C

### 2021-01-30 WOOT/Files/experiment.tex
Update

After collecting the captured videos of the mobile phone, we analyzed the videos both automatically and manually.
During the automatic analysis, we used scripts to perform OCR recognition for each frame in the recorded videos and stored all of the OCR results in a database.
In total, there are $94,058$ entries of data collected among 10 volunteers.
\shuqing{The data may need to be updated.}
With these results, we could learn what content the victim visited.
\fengwei{The following text needs to be revised. It is quite difficult for me to understand. Note that this is important text because reviewers are curious about the result. }
Additionally, keywords such as \textit{account, username, and password} often appear with users' input data because they are often used as labels of input boxes.
Such keywords are more likely to lead us to user-specific data.
For example, when we searched with \textit{account} as a keyword, victim's accounts can be found in the database, as shown in the Table~\ref{tab:ocr_keyword_example}.
\shuqing{Statistics.}
The frame number is the position of this frame in the recorded video, which indicates a target for manual analysis for further data extraction.

>>>>

After collecting the captured videos of the mobile phone, we analyzed the videos both automatically and manually.
During the automatic analysis, we used scripts to perform OCR recognition for each frame in the recorded videos and stored all of the OCR results in a database.
In total, there are $94,058$ entries of data collected among 10 volunteers.
%\shuqing{The data may need to be updated.}
With these results, we could learn what content the victim visited.
%\fengwei{The following text needs to be revised. It is quite difficult for me to understand. Note that this is important text because reviewers are curious about the result. }
Additionally, keywords such as \textit{account, username, and password} often appear with users' input data because they are often used as labels of input boxes.
Such keywords are more likely to lead us to user-specific data.
For example, when we searched with \textit{account} as a keyword, victim's accounts can be found in the database, as shown in the Table~\ref{tab:ocr_keyword_example}.
%\shuqing{Statistics.}
The frame number is the position of this frame in the recorded video, which indicates a target for manual analysis for further data extraction.
